Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-31 Draft/Draft.Rmd
Hopefully improving the intro

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@delmas2019; @simmons2019]. Intermediate levels that investigate plant-pollinator networks (meso-scale) have been little explored but can shed light on ecological processes not captured by the traditional approaches used in plant-pollinator network studies.

Research of plant-pollinator networks have proven common invariant structural properties across networks. Mutualistic networks tend to be nested [@bascompte2003], the degree distribution (number of links per species) generally follows a truncated power law distribution [@jordano2003] and there is an imbalance with approximately four times more pollinator species than plant species [@vazquez2009]. In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020]. Despite progress in plant-pollinator interactions, indirect interactions such as the competitive and facilitative interactions between plants for pollinators have been rarely investigated [@simmons2020]. However, the recent advances in analytical tools [..To be continued..]

Trait matching

>>>>

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the network structure have proven common invariant structural properties across them including nestedness [@jordano2003], the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009] and a degree distribution that decays as a power law [@jordano2003]. In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020]. However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].
